An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-01-19 EconGrowth2.Rnw
Small punctuation change.

In contrast to both the Cobb-Douglas model (Equations~\ref{eq:CD} and 
\ref{eq:CDe}) and the CES model (Equations~\ref{eq:CES}--\ref{eq:CESekl}), 
the LINEX model (Equation~\ref{eq:LINEX}) attempts to explain the residual ($A$)
with physical factors,
efficiencies among capital, labor, and energy.
Therefore, LINEX does not employ a time-dependent 
residual term ($A$).

>>>>

In contrast to both the Cobb-Douglas model (Equations~\ref{eq:CD} and 
\ref{eq:CDe}) and the CES model (Equations~\ref{eq:CES}--\ref{eq:CESekl}), 
the LINEX model (Equation~\ref{eq:LINEX}) attempts to explain the residual ($A$)
with physical factors:
efficiencies among capital, labor, and energy.
Therefore, LINEX does not employ a time-dependent 
residual term ($A$).
